Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-19 doc/JFLA2022/paper.tex
add paragraph summarizing proof engineering improvements

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that the first and last authors founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting open source \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries~\cite{CantorContrib,AdditionsContrib} (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq ecosystem.

@@

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime_HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

>>>>

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that the first and last authors founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting open source \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries~\cite{CantorContrib,AdditionsContrib} (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a preliminary bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq ecosystem.

@@

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime_HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition with the \equations
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

\paragraph{Proof engineering improvements.}
%
The original release of the Cantor library preceded support for type classes in \coq~\cite{MS08}. Changes over time before the move of \Hydras to \community have since then introduced type classes for some concepts in the Hydra-battles library related to ordinals. Most type classes initially used a \emph{semi bundled} approach~\cite{Mathlib}, but we have recently \emph{unbundled} some classes to enable more sharing during resolution~\cite{BS2011}. Due to the modest depth of our class hierarchy, we believe this will not lead to scalability issues. Orthogonally to type classes, we introduced additional automation for definitions via the \equations and Paramcoq plugins.
